Epidemic Tracking and Forecasting: Lessons Learned from a Tumultuous Year

### 2021-11-04 perspective/paper.tex
Add acks paragraph

\begin{enumerate}
\item \citet{Reinhart:2021} describes our group's (ongoing) effort in building
  and maintaining COVIDcast: an open repository of real-time, geographically
  detailed COVID-19 indicators in the U.S.  These indicators (a term we use
  interchangeably with signals) are derived from a diverse set of data sources:
  medical testing devices, medical insurance claims, internet search trends,
  app-based mobility data, and online surveys, among others.  Many indicators
  are demonstrated to have meaningful statistical relationships with what have
  become the pandemic's ``topline'' numbers (reported cases, hospitalizations,
  deaths), whereas others uniquely reflect certain activity (not available in
  other publicly-available data sources) that may drive or affect the spread of
  COVID-19.  The paper demonstrates through a number of examples that the
  indicators in the COVIDcast repository can improve on the timeliness,
  robustness, and scope of traditional public health reporting streams.

\item \citet{McDonald:2021} provides a detailed analysis of whether a core set
  of the indicators in the COVIDcast repository can be used to improve the
  accuracy of COVID-19 short-term forecasting and hotspot detection models.
  This speaks to the quantitative utility of the indicators in a way that is
  directly tied to the benefits observed in relevant downstream modeling tasks.
  The paper finds that time series models (that are already competitive with top
  forecasters from the COVID-19 Forecast Hub \citep{ForecastHub}) improve in
  predictive accuracy when they are supplemented with any of the five indicators
  under consideration.  However, the magnitude of these improvements varies with
  the pandemic's local dynamics at prediction time, and only one indicator
  appears to offer a nontrivial improvement during upswings.

\item \citet{Salomon:2021} focuses on the U.S. COVID-19 Trends and Impact Survey
  (CTIS), an (ongoing) online survey operated by our group, in partnership with
  Facebook.  This is a very rich source of data about the pandemic and its
  effect on people, only partially reflected by the indicators (derived from the
  survey) in the COVIDcast repository; the full data set of individual,
  anonymized survey responses is available to researchers under a data use
  agreement.  The paper presents descriptive analyses that reflect the unique
  value of CTIS as an important supplement to public health reporting, in
  particular, as an instrument to measure key information about behaviors,
  attitudes, economic impacts, and other topics not covered in traditional
  public health streams.

\item \citet{Astley:2021} focuses on the international version of CTIS, which is
  an (ongoing) online survey operated by the University of Maryland, again in
  partnership with Facebook.  This international survey covers over 100
  countries, and is run in coordination with the U.S. one, so that they bear a
  similar structure and undergo similar updates; the full data set of
  individual, anonymized survey responses is again available to individual
  researchers under a data use agreement.  The paper presents analyses that
  reflect some basic and important characteristics of the international survey,
  reflecting its value abroad, where public health reporting efforts may be more
  limited than those in the U.S.
\end{enumerate}

@@

While some aspects of mandated reporting are likely to remain irreplaceable,
effective alternative surveillance sources can be of great use: they can improve
on the timeliness, scope, robustness, and utility of mandated reporting data,
while being less burdensome to collect.  This is a common theme that runs
through all four papers in the collection, but is perhaps most directly
addressed in \citet{Reinhart:2021} (which focuses on the ecosystem of signals
broadly).  That said, we have far from saturated the utility of auxiliary
surveillance.  Much more needs to be developed in this area in order to usher
epidemic tracking into its next phase of reliability, accuracy, and
transparency.  To us, electronic medical records hold a great promise for
surveillance streams, and we elaborate on this in the next section.

@@

\emph{Authors' note: to be filled out later.}

>>>>

\begin{enumerate}
\item Reinhart et al.\ \citep{Reinhart:2021} describes our group's (ongoing)
  effort in building and maintaining COVIDcast: an open repository of real-time,
  geographically detailed COVID-19 indicators in the U.S.  These indicators (a
  term we use interchangeably with signals) are derived from a diverse set of
  data sources: medical testing devices, medical insurance claims, internet
  search trends, app-based mobility data, and online surveys, among others.
  Many indicators are demonstrated to have meaningful statistical relationships
  with what have become the pandemic's ``topline'' numbers (reported cases,
  hospitalizations, deaths), whereas others uniquely reflect certain activity
  (not available in other publicly-available data sources) that may drive or
  affect the spread of COVID-19.  The paper demonstrates through a number of
  examples that the indicators in the COVIDcast repository can improve on the
  timeliness, robustness, and scope of traditional public health reporting streams.

\item McDonald et al.\ \citep{McDonald:2021} provides a detailed analysis of
  whether a core set of the indicators in the COVIDcast repository can be used
  to improve the accuracy of COVID-19 short-term forecasting and hotspot
  detection models. This speaks to the quantitative utility of the indicators in
  a way that is directly tied to the benefits observed in relevant downstream
  modeling tasks. The paper finds that time series models (that are already
  competitive with top forecasters from the COVID-19 Forecast Hub
  \citep{ForecastHub}) improve in predictive accuracy when they are supplemented
  with any of the five indicators under consideration, based on COVID-related
  medical insurance claims, self-reported symptoms from surveys (in fact, from
  CTIS, described next), and COVID-related Google searches.

\item Salomon et al.\ \citep{Salomon:2021} focuses on the U.S. COVID-19 Trends 
  and Impact Survey (CTIS), an (ongoing) online survey operated by our group, in
  partnership with Facebook.  This is a very rich source of data about the
  pandemic and its effect on people, only partially reflected by the indicators
  (derived from the survey) in the COVIDcast repository; the full data set of
  individual, anonymized survey responses is available to researchers under a
  data use agreement.  The paper presents descriptive analyses that reflect the
  unique value of CTIS as an important supplement to public health reporting, in
  particular, as an instrument to measure key information about behaviors, 
  attitudes, economic impacts, and other topics not covered in traditional
  public health streams.

\item Astley et al.\ \citep{Astley:2021} focuses on the international version of
  CTIS, which is an (ongoing) online survey operated by the University of
  Maryland, again in partnership with Facebook.  This international survey
  covers over 100 countries and territories, and is run in coordination with the
  U.S.\ one, so that the two bear similar structures and undergo similar
  updates; the full data set of individual, anonymized international survey
  responses is again available to individual researchers under a data use
  agreement.  The paper presents analyses that reflect some basic and important
  characteristics of the international survey, reflecting its value abroad,
  where public health reporting efforts may be more limited than those in the
  U.S. 
\end{enumerate}

@@

While some aspects of mandated reporting are likely to remain irreplaceable,
effective alternative surveillance sources can be of great use: they can improve
on the timeliness, scope, robustness, and utility of mandated reporting data,
while being less burdensome to collect.  This is a common theme that runs
through all four papers in the collection, but is perhaps most directly
addressed in \citep{Reinhart:2021} (which focuses on the ecosystem of signals
broadly).  That said, we have far from saturated the utility of auxiliary
surveillance.  Much more needs to be developed in this area in order to usher
epidemic tracking into its next phase of reliability, accuracy, and
transparency.  To us, electronic medical records hold a great promise for
surveillance streams, and we elaborate on this in the next section.

@@

We thank Michael Finke, Dawn Rucker, and Nigam Shah for sustained counsel over 
the past year; Donald Rucker for educating us on Health Information Exchanges;
and Logan Brooks and Maria Jahja for their help assembling references for this
perspective. More broadly, we are grateful to the entire Delphi team whose work
is described in this special issue and is the basis for the lessons we discussed
here. Delphi's work from its inception was enabled, encouraged, and supported by 
the CDC's Influenza Division, and we are especially indebted to Matt
Biggerstaff, Michael Johansson, and Carrie Reed for many years of productive
collaboration and friendship. Lastly, Delphi's work would not be possible
without the invaluable data and support provided by our industry partners and
friends; a detailed list is given in the acknowledgements section of
\citep{Reinhart:2021}.

This material is based on work supported by gifts from Google.or and the McCune 
Foundation; and by Centers for Disease Control and Prevention (CDC) grant
U01IP001121.
